Target Markdown

### 2023-06-04 _targets.Rmd
updated databasea and added ids

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych"
                            ))

@@

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
     #          format = "qs"),
      tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
      tar_target(ids_complete, create_ids_complete(ids, db_path)),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete))

    # tar_target(all_pubs,
    #        get_all_pubs(db_path, ids_complete), 
    #           format = "qs"),
    # tar_target(one_author,
    #        read_one_author(db_path, ids_complete_vector, ids_complete), 
    #           format = "qs")
    # 
)
```

@@

      tar_target(matching, match(db_path, ids, gender)),
      tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
     #          format = "qs"),
      tar_target(final_data, refine_data(matching, db_path, ids, sup_control)),

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector)),
     tar_target(random_pubs,
           get_random_pubs(db_path))
)
```

@@

    # tar_target(edgelist,
    #            make_edgelist(one_author),
    #             format = "qs", pattern = map(one_author), iteration = "list"),
    # tar_target(graph, igraph::graph_from_data_frame(edgelist, directed = FALSE), pattern = map(edgelist), iteration = "list")
    tar_target(coauthorship,
               make_network(all_authors)),

@@

    # tar_target(eigen_centr,
    #            calc_eigen_centr(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list")
    # 
     tar_target(eigen_centrality,
               comp_eigen_centr(coauthorship_graph))

@@

    #  tar_target(clustering,
    #             calc_clustering(graph, ids_complete, one_author, db_path),
    #            format = "qs", pattern = map(graph, one_author), iteration = "list") 
    # #            
    # #

@@

     # tar_target(ind_pubs,
     #            calc_ind_pubs(one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author),                  iteration = "list")
     # 
     tar_target(independent_pubs,
                comp_ind_pubs(cluster))
)

@@

     # tar_target(ind_topics,
     #            calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
     #            format = "qs", pattern = map(one_author), iteration = "list")
     # 
    tar_target(independent_topics,
                comp_ind_topics(independent_pubs, topic_model, db_path))
)

@@

    # tar_target(final_data,
    #            calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs, matching),
    #            format = "qs") #,
    #  # tar_target(testing,
    #  #           just_test(db_path),
    #  #           format = "qs")

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI",
                            "MatchIt",
                            "qs",
                            "tidyverse",
                            "psych",
                            "arrow"
                            ))

@@

     tar_target(ids_path, here::here("data", "raw", "supervisors.csv"), format = "file"),
     tar_target(ids, read.csv2(ids_path)),
     tar_target(gender_path, here::here("data", "raw", "names4api_tagged.tsv"), format = "file"),
     tar_target(gender, read.delim(gender_path)),
     # tar_target(gender, read.delim(here::here("data", "raw", "names4api_tagged.tsv")),
     #          format = "qs"),
     tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
     tar_target(authors_arrow_path, here::here("data", "raw", "authors_by_pubs.arrow")),
     tar_target(authors_arrow, arrow::read_feather(authors_arrow_path)),
     tar_target(text_arrow_path, here::here("data", "raw", "riv_text.arrow")),
     tar_target(text_arrow, arrow::read_feather(text_arrow_path)),
     tar_target(ids_complete, create_ids_complete(ids, db_path)),
     tar_target(ids_complete_vector, make_ids_complete_vector(ids_complete))

@@

      tar_target(matching, match(db_path, ids, gender, authors_arrow)),
      tar_target(sup_path, here::here("data", "raw", "supervisors_control_final.csv"), format = "file"),
      tar_target(sup_control, read.csv2(sup_path)),

     # tar_target(sup_control, read.csv2(here::here("data", "raw", "supervisors_control.csv")),
     #          format = "qs"),
      tar_target(final_data, refine_data(matching, db_path, ids, sup_control, authors_arrow)),

     #at this point, I will need to manually search for the supervisors of the control group researchers and upload their vedidks into new ids file
     tar_target(ids_full_vector,
               make_ids_full_vector(matching)),
     tar_target(all_pubs,
           get_all_pubs(db_path, final_data, authors_arrow, text_arrow)),
    tar_target(all_authors,
           read_all_authors(db_path, ids_complete_vector, ids_complete, final_data, ids_full_vector, authors_arrow)),
     tar_target(random_pubs,
           get_random_pubs(db_path, authors_arrow, text_arrow))
)
```

@@

    tar_target(coauthorship,
               make_network(all_authors)),

@@

     tar_target(eigen_centrality,
               comp_eigen_centr(coauthorship_graph))

@@

@@

   tar_target(independent_pubs,
                comp_ind_pubs(cluster))
)

@@

    tar_target(independent_topics,
                comp_ind_topics(independent_pubs, topic_model, db_path, authors_arrow))
)

@@

    #  # tar_target(testing,
    #  #           just_test(db_path),
    #  #           format = "qs")
